---
title: "Customer Churn Report"
subtitle: "R-Tip 24: Rmarkdown Report with Shiny!"
author: "Business Science"
output: 
  html_document:
    theme: flatly
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE, 
  message = FALSE, 
  warning = FALSE
)
```

# Problem

Customer Churn is impacting revenue sales. What can we do?

# Solution

My analysis suggests that we can __reduce churn by moving customers to longer term contracts.__

```{r}
library(correlationfunnel)
library(tidyquant)
library(plotly)
library(tidyverse)
library(shiny)
```

## Contract Type Effect

Customer churn varies significantly by contract type. A potential strategy is to encourage purchasing long-term contracts versus month-to-month. 

```{r}
inputPanel(
  shiny::selectInput("chart_type", label = "Chart Type", 
                     choices = c("Customer-Level", "Aggregated"))
)
```

```{r}
output$p1 <- renderPlotly({
  
  if (input$chart_type == "Aggregated") {
    g <- customer_churn_tbl %>%
      select(Contract, Churn) %>%
      count(Contract, Churn) %>%
      group_by(Contract) %>%
      mutate(prop = n / sum(n)) %>%
      ungroup() %>%
      mutate(Contract = as_factor(Contract) %>% fct_reorder(prop) %>% fct_rev()) %>%
      filter(Churn == 'Yes') %>%
      ggplot(aes(prop, Contract)) +
      geom_col(aes(text = str_glue("Churn %: {scales::percent(prop)}")), 
               fill = palette_light()[2]) +
      scale_x_continuous(labels = scales::percent_format()) +
      theme_tq() 
  } else {
    g <- customer_churn_tbl %>%
      mutate(value = ifelse(Churn == 'Yes', 1, 0)) %>%
      mutate(Contract = factor(Contract, 
                               levels = c("Month-to-month", "One year", "Two year"))) %>%
      ggplot(aes(value, Contract, color = Churn)) +
      geom_jitter((aes(text = str_glue({
        "Customer ID: {customerID}
        Contract: {Contract}
        Tenure: {tenure}
        Payment Method: {PaymentMethod}"
      }))), 
                  alpha = 0.5) +
      scale_color_tq() +
      scale_x_continuous(breaks = c(0,1)) +
      theme_tq() +
      labs(x = "Churn Numeric (Yes = 1, No = 0)")
  }
  
   ggplotly(g)
})

plotlyOutput("p1", height = "600px")
```

## Feature Importance

```{r}
inputPanel(
  sliderInput("n_breaks", label = "Number of Bins (Numeric Features):",
              min = 2, max = 8, value = 4, step = 1)
)
```


```{r}
output$g1 <- renderPlot({
   customer_churn_tbl %>%
    select(-customerID) %>%
    replace_na(replace = list(TotalCharges = 0)) %>%
    binarize(
      n_bins        = input$n_breaks, 
      thresh_infreq = 0.05
    ) %>%
    correlate(target = Churn__Yes) %>%
    plot_correlation_funnel(interactive = FALSE) +
    geom_point(size = 3, alpha = 0.7, color = palette_light()[1])
})

plotOutput("g1", height = "600px")

br()
```

<div class="well">
# Learn Shiny

Businesses need scalable `shiny` applications. I have 2 courses:

1. [Beginner: Shiny Dashboards](https://university.business-science.io/p/ds4b-102-r-shiny-web-application-business-level-1)

2. [Expert: Shiny Developer with AWS](https://university.business-science.io/p/expert-shiny-developer-with-aws-course-ds4b-202a-r)

Course are part of the [Business Science R-Track Program](https://www.business-science.io/courses.html). 

</div>
