---
title: "Intro to Interactive Slide Decks | Xaringan"
subtitle: "Let's do this"
author: "Matt Dancho"
institute: "Business Science"
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: arta
      highlightLines: true
      countIncrementalSlides: false
---



```{r setup, include=FALSE}
options(
  htmltools.dir.version  = FALSE,
  htmltools.preserve.raw = FALSE # needed for windows
)
```


# Awesome Title

Here is some text. 

- Bullet 1
- Bullet 2

``` r
code <- "awesome"
```

And don't forget to set up __Infinite Moon Reader RStudio Addin!__

---
# New Slide

This is a simple introduction to Xaringan

---
class: top, center

#  Top Center

More stuff

.left[And more]

.right[And right]

---
# Incremental Reveals

--

Next

--

Next

--

One final piece

---

# Two-Columns

.pull-left[

## Column 1

- First Bullet

]

.pull-right[

## Column 2

- First Comparison

]

---

# Code Highlight & Tables

```{r, echo=T}
library(tidyverse)

mpg %>%
  knitr::kable()
```

---

# DT Tables

```{r}
library(DT)

mpg %>% DT::datatable()
```

---

# Maps

```{r, out.width="100%", warning=F}
library(leaflet)

leaflet() %>%
  setView(lng = -71.0589, lat = 42.3601, zoom = 12) %>%
  addProviderTiles(providers$Esri.NatGeoWorldMap)
```

---

# Plots

```{r, out.width="100%", out.height="70%"}
library(timetk)

m4_monthly %>%
  plot_time_series(date, value, .facet_vars = id, .facet_ncol = 2)
```

---
# Side-by-Side

.pull-left[

Let's check out the monthly seasonality. 

```{r}
library(timetk)

p <- m4_monthly %>%
  filter(id == "M750") %>%
  plot_time_series(
    .date_var   = date, 
    .value      = value
  )
```

]

.pull-right[
```{r, echo=F, out.width="100%"}
p
```


]

---

# Themes

```{r}
names(xaringan:::list_css())
```



---

# Lot's more!

- [_"Meet xaringan"_: Allison Hill's RStudio 2019 Conf Talk](https://arm.rbind.io/slides/xaringan.html)

- [_"Applying design guidelines to slides with {xaringanthemer}"_: By Katie Jolly](https://www.katiejolly.io/blog/2021-03-16/designing-slides)

- [_"Presentation Ninja with xaringan"_ by Yihui Xie](https://slides.yihui.org/xaringan/#1)

.center[
  ![](https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
]



