---
title: "Word Automation"
author: "Business Science"
date: "2023-02-07"
output: officedown::rdocx_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    # Table Captioning
    tab.cap.style = "Table Caption",
    tab.cap.pre = "Table ",
    tab.cap.sep = ": ",
    # Figure Captioning
    fig.cap.style = "Image Caption",
    fig.cap.pre = "Figure ",
    fig.cap.sep = ": "
)

# LIBRARIES
library(officedown)
library(officer)
library(tidyverse)
library(timetk)
```

## Executive Summary

This document tracks the economics data of US population and unemployment.

\newpage

## Table of Contents

```{r}
block_toc()
```
## Table of Figures

```{r}
block_toc(style = "Image Caption")
```

\newpage

## Figures

This is a linked reference to a figure \@ref(fig:tsplot), its number is computed by Word 
and it's linked to the corresponding graphic when clicking on it.

```{r fig.cap="economics plot", fig.id = "tsplot", fig.cap.style = "Image Caption"}
economics %>%
    plot_time_series(
        .date_var    = date, 
        .value       = unemploy / pop,
        .interactive = FALSE
    )
```

## Tables

This is a linked reference to a table \@ref(tab:mytab), its number is computed by Word 
and it's linked to the corresponding table when clicking on it.

```{r tab.cap="economics table", tab.id = "mytab", tab.cap.style = "Table Caption"}
head(economics)
```


